Demand Forecasting of individual Probability Density Functions with Machine Learning

### 2020-08-08 LaTex/paper.tex
small feature set fix

In this model focusing on the variance, we use a different set of features: categorical variables for \texttt{store\_id} and \texttt{item\_id} and a flag denoting a promotion. An example for the resulting PDF and CDF predictions for item \texttt{FOODS\_3\_586} in store \texttt{WI\_1} on 2016-05-22 is shown in \fig \ref{fig:pdf_example}.

>>>>

In this model focusing on the variance, we use the same set of features as for the mean model described above in sec. \ref{sec:example_mean}, except for dropping the two-dimensional combinations including individual event features. An example for the resulting PDF and CDF predictions for item \texttt{FOODS\_3\_586} in store \texttt{WI\_1} on 2016-05-22 is shown in \fig \ref{fig:pdf_example}.
